Comparing Predicted Boundaries vs Called Boundaries

### 2019-08-09 Scripts/evaluating_thresholds_for_pred_bounds.Rmd
initial commit

>>>>

## GM12878; chr21

```{r}
toptfbs_mean_gm12878_chr21 <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR21/smote/distance/enet/called_and_pred_bound_regions.rds")

res <- makeVennDiagram(Peaks=list(toptfbs_mean_gm12878_chr21[[3]], toptfbs_mean_gm12878_chr21[[4]]),
                       NameOfPeaks=c("Called", "Predicted"),
                       connectedPeaks = "keepAll")
venn_gm12878_22 <- venn_cnt2venn(res$vennCounts)
venn_gm12878_22 <- compute.Venn(venn_gm12878_22)
gp <- VennThemes(venn_gm12878_22)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, 
                                                 gp = gp, 
                                                 show=list(Universe=FALSE))), 
                        top=textGrob("Boundary Region", 
                                     gp=gpar(fontsize=50)))

sh <- unique(subjectHits(findOverlaps(toptfbs_mean_gm12878_chr21[[3]], toptfbs_mean_gm12878_chr21[[4]])))
pbnc <- toptfbs_mean_gm12878_chr21[[4]][-sh]

pbnc_to_ctcf <- GenometriCorrelation(pbnc,
                                     annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"], 
                                     chromosomes.length = max(end(pbnc),
                                                              end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"])),
                                     chromosomes.to.proceed = "chr21", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

pbnc_to_rad21 <- GenometriCorrelation(pbnc,
                                      annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"], 
                                      chromosomes.length = max(end(pbnc),
                                                               end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"])),
                                      chromosomes.to.proceed = "chr21", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

pbnc_to_smc3a <- GenometriCorrelation(pbnc,
                                      annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"], 
                                      chromosomes.length = max(end(pbnc),
                                                               end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"])),
                                      chromosomes.to.proceed = "chr21", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

pbnc_to_znf143 <- GenometriCorrelation(pbnc,
                                       annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"], 
                                       chromosomes.length = max(end(pbnc),
                                                                end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"])),
                                       chromosomes.to.proceed = "chr21", 
                                       permut.number = 100,
                                       ecdf.area.permut.number = 100,
                                       mean.distance.permut.number = 100,
                                       jaccard.measure.permut.number = 100,
                                       keep.distributions = TRUE, 
                                       showProgressBar = TRUE)

#PAC
sh <- unique(subjectHits(findOverlaps(toptfbs_mean_gm12878_chr21[[3]], toptfbs_mean_gm12878_chr21[[4]])))
pac <- toptfbs_mean_gm12878_chr21[[4]][sh]

pac_to_ctcf <- GenometriCorrelation(pac,
                                    annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"], 
                                    chromosomes.length = max(end(pac),
                                                             end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"])),
                                    chromosomes.to.proceed = "chr21", 
                                    permut.number = 100,
                                    ecdf.area.permut.number = 100,
                                    mean.distance.permut.number = 100,
                                    jaccard.measure.permut.number = 100,
                                    keep.distributions = TRUE, 
                                    showProgressBar = TRUE)

pac_to_rad21 <- GenometriCorrelation(pac,
                                     annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"], 
                                     chromosomes.length = max(end(pac),
                                                              end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"])),
                                     chromosomes.to.proceed = "chr21", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

pac_to_smc3a <- GenometriCorrelation(pac,
                                     annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"], 
                                     chromosomes.length = max(end(pac),
                                                              end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"])),
                                     chromosomes.to.proceed = "chr21", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

pac_to_znf143 <- GenometriCorrelation(pac,
                                      annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"], 
                                      chromosomes.length = max(end(pac),
                                                               end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"])),
                                      chromosomes.to.proceed = "chr21", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

#CAP
qh <- unique(queryHits(findOverlaps(toptfbs_mean_gm12878_chr21[[3]], toptfbs_mean_gm12878_chr21[[4]])))
cap <- toptfbs_mean_gm12878_chr21[[3]][qh]

cap_to_ctcf <- GenometriCorrelation(cap,
                                    annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"], 
                                    chromosomes.length = max(end(cap),
                                                             end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"])),
                                    chromosomes.to.proceed = "chr21", 
                                    permut.number = 100,
                                    ecdf.area.permut.number = 100,
                                    mean.distance.permut.number = 100,
                                    jaccard.measure.permut.number = 100,
                                    keep.distributions = TRUE, 
                                    showProgressBar = TRUE)

cap_to_rad21 <- GenometriCorrelation(cap,
                                     annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"], 
                                     chromosomes.length = max(end(cap),
                                                              end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"])),
                                     chromosomes.to.proceed = "chr21", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

cap_to_smc3a <- GenometriCorrelation(cap,
                                     annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"], 
                                     chromosomes.length = max(end(cap),
                                                              end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"])),
                                     chromosomes.to.proceed = "chr21", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

cap_to_znf143 <- GenometriCorrelation(cap,
                                      annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"], 
                                      chromosomes.length = max(end(cap),
                                                               end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"])),
                                      chromosomes.to.proceed = "chr21", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

#CBNP
qh <- unique(queryHits(findOverlaps(toptfbs_mean_gm12878_chr21[[3]], toptfbs_mean_gm12878_chr21[[4]])))
cbnp <- toptfbs_mean_gm12878_chr21[[3]][-qh]

cbnp_to_ctcf <- GenometriCorrelation(cbnp,
                                     annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"], 
                                     chromosomes.length = max(end(cbnp),
                                                              end(annots.GR[[1]][seqnames(annots.GR[[1]])=="chr21"])),
                                     chromosomes.to.proceed = "chr21", 
                                     permut.number = 100,
                                     ecdf.area.permut.number = 100,
                                     mean.distance.permut.number = 100,
                                     jaccard.measure.permut.number = 100,
                                     keep.distributions = TRUE, 
                                     showProgressBar = TRUE)

cbnp_to_rad21 <- GenometriCorrelation(cbnp,
                                      annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"], 
                                      chromosomes.length = max(end(cbnp),
                                                               end(annots.GR[[2]][seqnames(annots.GR[[2]])=="chr21"])),
                                      chromosomes.to.proceed = "chr21", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

cbnp_to_smc3a <- GenometriCorrelation(cbnp,
                                      annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"], 
                                      chromosomes.length = max(end(cbnp),
                                                               end(annots.GR[[3]][seqnames(annots.GR[[3]])=="chr21"])),
                                      chromosomes.to.proceed = "chr21", 
                                      permut.number = 100,
                                      ecdf.area.permut.number = 100,
                                      mean.distance.permut.number = 100,
                                      jaccard.measure.permut.number = 100,
                                      keep.distributions = TRUE, 
                                      showProgressBar = TRUE)

cbnp_to_znf143 <- GenometriCorrelation(cbnp,
                                       annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"], 
                                       chromosomes.length = max(end(cbnp),
                                                                end(annots.GR[[4]][seqnames(annots.GR[[4]])=="chr21"])),
                                       chromosomes.to.proceed = "chr21", 
                                       permut.number = 100,
                                       ecdf.area.permut.number = 100,
                                       mean.distance.permut.number = 100,
                                       jaccard.measure.permut.number = 100,
                                       keep.distributions = TRUE, 
                                       showProgressBar = TRUE)
